The Analog Method for Precipitation Prediction: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-11-24 Moving temporal window - HESS/template.tex
My last HESS corrections.

%TODO: check figs and table captions
%TODO: order figs
%TODO: english editing
%TODO: analogs
%TODO: perspective Obled: MTW without precip -> indicator

@@

\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analyzed the influence of the archive length on the quality of the analogy. They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive. They demonstrate that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude). For that reason, smaller spatial windows are always considered to search for analogues, and the archive length is maximized.

@@

\begin{figure*}[htb]
	\begin{center}
		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
	\end{center}
	\caption{Changes in the S1 criterion distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
	\label{fig:changes_S1_analogs}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the S1 distributions with and without the MTW. (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
	\label{fig:changes_S1}
\end{figure}

@@

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
	\label{fig:changes_RMSE}
\end{figure}

@@

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}

>>>>

%TODO: english editing
%TODO: perspective Obled: MTW without precip -> indicator

@@

\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analyzed the influence of the archive length on the quality of the analogy. They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive. They demonstrate that it is not possible to find good analogs on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude). For that reason, smaller spatial windows are always considered to search for analogs, and the archive length is maximized.

@@

\begin{figure*}[htb]
	\begin{center}
		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
	\end{center}
	\caption{Changes in the S1 criterion distributions, due to the MTW, of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station.}
	\label{fig:changes_S1_analogs}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog. (a) Quantiles of the S1 distributions with and without the MTW. (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
	\label{fig:changes_S1}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
	\label{fig:changes_RMSE}
\end{figure}

@@

@@

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:calibration}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}
